Ricci-Ollivier Curvature of the Rooted Phylogenetic Subtree-Prune-Regraft Graph

### 2015-07-24 curvature.tex
Better explanation of regression p-values.

\begin{table}
\centering
\caption{Ordinary least squares linear multiple regression of rSPR mean access time against degree and distance.}
\csvautotabular{tables/mean-access.csv}}
\label{tab:regressionMAT}
\end{table}

@@

\begin{table}
\centering
\caption{Ordinary least squares linear multiple regression of rSPR $\delta_1$ against degree, distance, and $\kappa$.}
\csvautotabular{tables/delta1.csv}}
\label{tab:regressionDelta}
\end{table}

>>>>

\begin{table}
\centering
\caption{p-values for ordinary least squares linear multiple regression of rSPR mean access time against degree and distance (two-tailed $t$-test of regression coefficient).}
\csvautotabular{tables/mean-access.csv}}
\label{tab:regressionMAT}
\end{table}

@@

\begin{table}
\centering
\caption{p-values for ordinary least squares linear multiple regression of rSPR $\delta_1$ against degree, distance, and $\kappa$ (two-tailed $t$-test of regression coefficient).}
\csvautotabular{tables/delta1.csv}}
\label{tab:regressionDelta}
\end{table}
